Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-07 edubots_surveys.Rnw
Reinstitutes eliminated citation

This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement. Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.

>>>>

This opens the door to the introduction of \textit{chatbots}, that is, autonomous agents able to communicate and interact with humans (or other chatbots) in a natural way \cite{Gong2008,differ.chat}, answering question and even posing their own ones to the user, in the classroom; in this limited environment, chatbots can appear as regular users, thus being close to passing a Turing Test \cite{moor2003turing}, which gives them certain characteristics that, again, can enhance student engagement. Chatbots implement different Artificial Intelligence techniques, such as natural language processing as well as, in some cases, learning; this is not a requirement, however, and in most cases they are simply applications that have a conversational interface, as opposed to a graphical user interface.
